Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-25 Paper/Paper.tex
slight improvement

Figure \ref{fig:encodesong} shows a typical example of encoding a song
using the codebook described in Section \ref{sec:codebook}.  Both the
Echo Nest chroma features for an example song and the corresponding
quantization are displayed.  The quantized representation retains
dominant harmonic structure of the original features, but is smoothed
in time due to the use of 2 bar long codewords.
%
This is consistent with the codebook described in Section
\ref{sec:codebook} which primarily consists of sustained chords across
4 or 8 beats.

@@

Since the clustering described in Section \ref{sec:approach} is based
on the segmentation of the signal in to bars, it stands to reason that
the cluster centroids should contain information related to bar
alignment, such as the presence of a strong beat on the first beat.
%
In this section we investigate whether it is possible to recover the
bar segmentation of new songs using the information contained in the
cluster centroids.  The results are shown Table \ref{tab:offset}. We find
the right segment with an accuracy of $62\%$ where random is
$25\%$. Details of the experiment follow.

@@

We apply our codebook to the artist recognition task.
Our dataset, ``artist20'', encompass $1402$ songs from $20$ artists, 
mostly rock and pop of different subgenres. Results exist in the
literature for that set \cite{Ellis2007}. The best accuracy is
$59\%$, whereas using only chroma as a representation yields an
accuracy of $33\%$. The latter results is obtained through a
Gaussian mixture model.

>>>>

Figure \ref{fig:encodesong} shows an example of a song encoded
using the codebook described in Section \ref{sec:codebook}.  Both the
Echo Nest chroma features for an example song and the corresponding
quantization are displayed.  The quantized representation retains
dominant harmonic structure of the original features, but is smoothed
in time due to the use of 2 bar long codewords.
%
This is consistent with the codebook described in Section
\ref{sec:codebook} which primarily consists of sustained chords across
4 or 8 beats.

@@

Since the clustering described in Section \ref{sec:approach} is based
on the segmentation of the signal in to bars, it stands to reason that
the cluster centroids should contain information related to bar
alignment, such as the presence of a strong beat on the first beat.
%
We investigate whether it is possible to recover the
bar segmentation of new songs using the information contained in the
cluster centroids.  The results are shown Table \ref{tab:offset}. We find
the right segment with an accuracy of $62\%$ where random is
$25\%$. Details of the experiment follow.

@@

We apply our codebook to the artist recognition task.
Our dataset, ``artist20'', encompass $1402$ songs from $20$ artists, 
mostly rock and pop of different subgenres. Results exist in the
literature for that set \cite{Ellis2007}. The best accuracy is
$59\%$, whereas using only chroma and a Gaussian mixture model
yields an accuracy of $33\%$.
